How the model was fit.

```{r}
library(devtools)
devtools::install_github("Gibbsdavidl/ImmuneSubtypeClassifier")

library(ImmuneSubtypeClassifier)
library(readr)
```

First we read in the PanCancer expression matrix,
'EBPlusPlusAdjustPANCAN_IlluminaHiSeq_RNASeqV2.geneExp.tsv'.

```{r}
download_file(src='http://api.gdc.cancer.gov/data/3586c0da-64d0-4b74-a449-5ff4d9136611', dest='~/ebpp.tsv')
ebpp <- read_tsv('~/ebpp.tsv')
```

Then we get the reported TCGA immune subtypes.

```{r}
reportedScores <- read_tsv('data/five_signature_mclust_ensemble_results.tsv.gz') # in the package data dir
reportedScores <- as.data.frame(reportedScores)
rownames(reportedScores) <- str_replace_all(reportedScores$AliquotBarcode, pattern = '\\.', replacement = '-')
```

A little processing on the EB++ gene identifiers

```{r}
geneList <- str_split(ebpp$gene_id, pattern='\\|')
geneSymbols <- unlist( lapply(geneList, function(a) a[2]) )
```

To get the matrix and phenotypes in the same order:

```{r}
X <- ebpp[, rownames(reportedScores)]
rownames(X) <- geneSymbols
Xmat <- as.matrix(X)
Y <- reportedScores[,"ClusterModel1"]
```

At this point you can do feature subsetting, or provide all features
and a rank sum test will reduce the total number.

To fit the ensemble model (list of subtype models):

```{r}
xbgParams <- list(max_depth = 5, eta = 0.3, nrounds = 150, nthread = 5, nfold=5, subsample=0.80)
ens <- fitEnsembleModel(Xmat, Y, n=10, sampSize=0.8, breakVec=c(0, 0.25, 0.5, 0.75, 1.0), params=xbgParams)
    ```

See scripts in the test directory for more detailed instructions on
fitting one subtype model, a model per subtype, or ensembles of models.

Additional fitted models are found in Inst/models

